\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2011-03-09 inst/doc/MSnbase-demo.Rnw
LazyData and NEWS
MSnProcess has not initialize(), changed MSnbase-demo and man to reflect truncated dummy data (size requirements)

<<MSnExp,cache=FALSE,echo=TRUE>>=
library(MSnbase)
filename <- dir(system.file(package="MSnbase",dir="extdata"),full.name=TRUE,pattern="mzXML$")
experiment <- readMzXMLData(filename, msLevel = 2, verbose=FALSE)
experiment
@

@@

<<Spectrum,cache=FALSE,echo=TRUE>>=
sp <- experiment[["X66"]]
sp
@

@@

<<ReporterIons>>=
data(iTRAQ4)
iTRAQ4
@

@@

<<extractPrecSpec,echo=T,cache=F>>=
exp2 <- extractPrecSpectra(experiment,precursorMz(experiment)["X66"])
exp2
@

@@

<<removePeaks,echo=TRUE,cache=FALSE>>=
experiment <- removePeaks(experiment,t=3,verbose=FALSE)
## total ion current
tic(sp)
tic(experiment[["X66"]])
@

\begin{figure}[!ht]
<<spectrum-plot2,fig=T,echo=T,tikz=T,external=T,width=5,height=5>>=
plot(experiment[["X66"]],reporters=iTRAQ4,full=TRUE)
@ 
\caption{Same spectrum as on figure \ref{fig:spectrum-plot}, after setting peaks <= 5 to 0.}
\label{fig:spectrum-plot2}
\end{figure}

@@

<<clean,echo=TRUE,cache=FALSE>>=
## number of peaks
peaksCount(sp)
peaksCount(experiment[["X66"]])
experiment <- clean(experiment,verbose=FALSE)
peaksCount(experiment[["X66"]])
@

@@

<<trimMz,echo=TRUE,cache=FALSE>>=
range(mz(sp))
experiment <- trimMz(experiment,mzlim=c(112,120))
range(mz(experiment[["X66"]]))
experiment
@

>>>>

<<MSnExp,cache=FALSE,echo=TRUE>>=
library(MSnbase)
filename <- dir(system.file(package="MSnbase",dir="extdata"),
                full.name=TRUE,pattern="mzXML$")
print(filename)
experiment <- readMzXMLData(filename, msLevel = 2, verbose=FALSE)
experiment
@

@@

<<Spectrum,cache=FALSE,echo=TRUE>>=
sp <- experiment[["X43"]]
sp
@

@@

<<ReporterIons>>=
iTRAQ4
@

@@

<<extractPrecSpec,echo=T,cache=F>>=
exp2 <- extractPrecSpectra(experiment,precursorMz(experiment)["X43"])
exp2
@

@@

<<removePeaks,echo=TRUE,cache=FALSE>>=
experiment <- removePeaks(experiment,t=3,verbose=FALSE)
## total ion current
tic(sp)
tic(experiment[["X43"]])
@

\begin{figure}[!ht]
<<spectrum-plot2,fig=T,echo=T,tikz=T,external=T,width=5,height=5>>=
plot(experiment[["X43"]],reporters=iTRAQ4,full=TRUE)
@ 
\caption{Same spectrum as on figure \ref{fig:spectrum-plot}, 
  after setting peaks <= 3 to 0.}
\label{fig:spectrum-plot2}
\end{figure}

@@

<<clean,echo=TRUE,cache=FALSE>>=
## number of peaks
peaksCount(sp)
peaksCount(experiment[["X43"]])
experiment <- clean(experiment,verbose=FALSE)
peaksCount(experiment[["X43"]])
@

@@

<<trimMz,echo=TRUE,cache=FALSE>>=
range(mz(sp))
experiment <- trimMz(experiment,mzlim=c(112,120))
range(mz(experiment[["X43"]]))
experiment
@
